\documentclass[margin,line]{resume}

\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx,wrapfig}
\usepackage{url}
\usepackage[colorlinks=true, pdfstartview=FitV,
linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

\usepackage{etoolbox}
\usepackage{xunicode}
\usepackage{xltxtra}
\usepackage{setspace}

\usepackage{mathpazo}

\defaultfontfeatures{Scale=MatchLowercase,Mapping=tex-text}
\frenchspacing

\setromanfont[Ligatures={Common}, Numbers={OldStyle}]{Minion Pro}

\topmargin=0mm
\textheight=235mm

\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}

\newcommand{\sth}[0]{\superscript{\scriptsize{th}}}
\newcommand{\sst}[0]{\superscript{\scriptsize{st}}}
\newcommand{\snd}[0]{\superscript{\scriptsize{nd}}}
\newcommand{\srd}[0]{\superscript{\scriptsize{rd}}}

\begin{document}

{\sc \Large Joseph E. Beaver}

\begin{resume}

	\section{\mysidestyle Personal\\ Information}\vspace{1em}
	\hspace{-0.5em}\begin{tabular}[t]{p{0.6\textwidth} r}
		\textbf{Joseph E. Beaver} & joseph.beaver@gmail.com \\
		192 Victoria Avenue,      & 07814 056 319           \\
		Borrowash                 &                         \\
		Derby                     &                         \\
		DE72 3HG                  &
	\end{tabular}

	\section{\mysidestyle Security Clearance}
	\begin{description}
		\item[SC] issued 01/2012
	\end{description}

	\section{\mysidestyle Experience}\vspace{1mm}

	\begin{description}

		\item[September 2022--] Rolls-Royce Plc. Senior Data Scientist

		\item[Experience] Technical Lead
		\item[Skills] project planning, infrastructure, architectural design,
		      detailed design, testing (\textsc{ISTQB} accredited),
		      coaching, training, \texttt{Mermaid},
		      \texttt{UML}, \texttt{SQLite}, \texttt{SQLServer},
		      \texttt{Python} (\texttt{numpy}, \texttt{scipy},
		      \texttt{plotly}, \texttt{dash}, \texttt{streamlit},
		      \texttt{stdlib}, \texttt{watchdog}, \texttt{fastapi},
		      \texttt{strawberry}, \texttt{sqlalchemy}, \texttt{pandera},
		      \texttt{pydantic}, \texttt{pandas}, \texttt{polars},
		      \texttt{xarray}, \texttt{matplotlib},\linebreak\texttt{scikit-learn},
		      \texttt{mkdocs}, \texttt{h5py}, \texttt{pytest}, \texttt{mock}),
		      \texttt{GraphQL}, in-code documentation, user documentation,
		      \texttt{Azure DevOps}, \texttt{VSCode},
		      \texttt{Windows Subsystem for Linux}, \texttt{Ubuntu}, \texttt{docker}, \texttt{bash},
		      \texttt{parquet}, code review, refactoring, domain-driven modelling,
		      data cleaning, visualisation, influence.
		\item[Responsibilities] Technical lead for automated data ingestion
		      service, GraphQL API, boat health monitoring analytics pipeline.
		      Upskill team members in quality assurance, technical skills,
		      tech stack, ways of working, developer mentality, planning,
		      design, and testing.
		      Company-wide influence on artefact configuration, ways of working,
		      developer skills for automation, use of \textsc{AI}/\textsc{ML}.
		      Interview panel experience.

		\item[Experience] Product Owner
		\item[Skills] project planning, coaching, training, stakeholder engagement
		      documentation, \texttt{Azure DevOps}, code review,
		      Agile, Scrum, sprint planning/review/retrospective.
		\item[Responsibilities] Product Owner for a team of 8.
		      Team worked on 5 produts simultaneously, 3 of which were of critical significance,
		      and handled emergent digital issues across the entire business.

		\item[Experience] Senior Data Scientist
		\item[Skills] see 'Tech Lead'
		\item[Responsibilities] investigation into predictive analytics methods.
		      Implementation of standardised timeseries data cleaning algorithms.


		\item[November 2019--September 2022] Rolls-Royce Plc. Methods Development Engineer

		\item[Experience] Methods Development Engineer
		\item[Skills] See 'Tech Lead'. Additionally: \texttt{C++},
		      \texttt{GoogleTest}, \texttt{CMake}, \texttt{hdf5}.
		\item[Responsibilities] Frontrunner for use of Agile practices;
		      test-project was completed 30\% ahead of schedule
		      and 20\% under budget.
		      External collaborative work with overseas business partners
		      on new archival data format.
		      Secondment to Structural Integrity team to trial use of \textsc{ML},
		      for predictive analytics on corrosion growth prediction.
		      Secondment to Core Producibility to enhance functionality
		      of reactor core component placement optimisation algorithms.
		      Business Unit consultant for software projects.
		      Subcontractor management.

		\item[Januar 2012--November 2019] Rolls-Royce Plc. Core Physics Design Engineer

		\item[Experience] Core Physics Design Engineer
		\item[Skills] \texttt{MatLab}, \texttt{Microsoft Office},
		      \texttt{SAP}, \texttt{Siemens Teamcenter}, \texttt{Redhat},
		      \texttt{AWK}, \texttt{SED}, \texttt{VI}, \texttt{tmux}, general command-line tools,
		      \texttt{csh}, experimental engineering.
		\item[Responsibilities] General automations.
		      Physics Test Assistant Supervisor; naval liaison, dockyard experiment management,
		      test equipment management, site security liaison.
		      Physical modelling and simulation of contemporary and historic naval reactor cores.
		      Automated Verification and Validation process.
		      Created archival experimental data storage format and database.
		      Created and maintained automated experimental physics analysis suite;
		      object-oriend GUI development in \texttt{MatLab}.
		      Company-wide training course development and delivery.
		      External industrial lecturer to Universities of Cambridge, Oxford, Birmingham,
		      Nottingham, York, and Imperial College London.
		      Recruitment experience at on- and off-site events.
		      Lead campaign for the acquisition and role-out of \texttt{Anaconda} suite.

	\end{description}


	\section{\mysidestyle Education}\vspace{1mm}

	\begin{description}

		\item[Master of Science from University of Birmingham] (2011-2012)
		      \textbf{Merit}. Industrial placement in \textsc{CDM}'s \textsc{RAOP}s
		      team doing work for Advanced Concepts on validating MONK criticality
		      benchmarks for thorium-based critical systems.

		\item[Masters in Physics with Philosophy (MPhys) from the University of York]
		      (2006--2010) \linebreak Result: \textbf{2.1}. Final project:
		      \textit{Quantum Mirrors for Cold Atoms and Bose-Einstein
			      Condensates}; computational modelling of slow atoms \& Bose-Einstein
		      condensates incident on a variety of potential surfaces.

	\end{description}

	\section{\mysidestyle Professional Memberships}\vspace{1mm}

	\begin{description}

		\item[Professional Institutes] Member of the Institute of Physics
		      (IoP).  Member of the IoP Science \& Innovation Committee
		      2016--2020. Co-chair and founder of the Early Career Researcher
		      special interest group. Early Career Researcher secretary.

	\end{description}

	\section{\mysidestyle References}\vspace{1mm}

	\begin{description}

		\item References available upon request.

	\end{description}

\end{resume}

\end{document}
